Wireless service accounting based on Ethereum state channels - Master Thesis

### 2019-10-25 Paper.tex
Add automation comments

@@

\subsubsection{Smart contract}
\subsubsection{Front-end} \label{ch:front-end}
\subsubsection{Back-end} \label{ch:back-end}

% \subsection{Implementation} \label{ch:implementation}

@@

\subsection{Regulation considerations} \label{ch:regulation}

TODO; talk about GDPR, telco KyC, european market regulation, etc.

>>>>

Main motivation to include a smart contract approach to the 5G
business model has direct correlation with securing and
automating all economical transactions according some pre-established
set of rules. In addition, automating as much as possible the
accounting and KyC layer relying on blockchain accounting smart
contract and identity systems (using blockchain as a Public Key
Infrastructure) can impact on a huge reduction of the overhead costs
of operators and neutral host providers lowering entrance barriers and
reducing market's friction.  This way, all the actors implied can
reduce bureaucracy costs and focus on their main activities providing
innovative good quality services to their customers and at the same
time keep a high standard regarding transparency and flexibility.

@@

@@

%% \subsection{Regulation considerations} \label{ch:regulation}

%% \vspace{0.35cm}

%% TODO; talk about GDPR, telco KyC, european market regulation, etc.
